Online Laterality Battery Pre-Processing - short version

### 2020-02-03 battery-preprocessing_v3_DB.Rmd
fixed an error in computing mean accuracy for Chimeric faces and RDT task

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# libraries 
library(readr)
library(yarrr)
library(dplyr)
library(tidyr)
library(car)
library(ggplot2)
library(knitr)
require(readr)  # for read_csv()
require(dplyr)  # for mutate()
require(tidyr)  # for unnest()
require(purrr)  # for map(), reduce()
library(GGally)
require(stringr) # string matching
```

@@

    temp_dat$subject[myrow] <- subname # add row for subject
    temp_dat$side[myrow] <- latlist[j] # add row for side
    temp_dat$accurate[myrow] <- sum(tmp$Correct,na.rm=TRUE) # add row for N accurate response
    temp_dat$p.corr[myrow] <- 100*mean(tmp$Correct,na.rm=TRUE) # add row for %accurate responses - NB for chimeric only error is wrong emotion - measure is just a measure of choice. For RDT, can make error of selecting wrong side, so % correct is meaningful

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# libraries 
library(readr)
library(yarrr)
library(dplyr)
library(tidyr)
library(car)
library(ggplot2)
library(knitr)
require(readr)  # for read_csv()
require(dplyr)  # for mutate()
require(tidyr)  # for unnest()
require(purrr)  # for map(), reduce()
library(GGally)
require(stringr) # string matching

@@

    temp_dat$subject[myrow] <- subname # add row for subject
    temp_dat$side[myrow] <- latlist[j] # add row for side
    temp_dat$accurate[myrow] <- sum(tmp2$Correct,na.rm=TRUE) # add row for N accurate response
    temp_dat$p.corr[myrow] <- 100*mean(tmp2$Correct,na.rm=TRUE) # add row for %accurate responses - NB for chimeric only error is wrong emotion - measure is just a measure of choice. For RDT, can make error of selecting wrong side, so % correct is meaningful
